---
title: "Systematic Sampling"
author: "Ane"
date: "October 30, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

Load necessary packages first
```{r}
library(survey)
```

#Question 1

```{r}
#When you run the code below, a pop-up window will show
#Get to the folder where the data is and select the data file
#policy = read.csv(file.choose()) # New Policy
policy = read.csv("")

head(policy)
```

#1b

```{r}
#Get summary measures
table(policy$FavorPolicy)
nrow(policy)
```


#1c

```{r}
#Add a variable to the data set "policy" with the population size
policy$N = 2000
head(policy)

#Specify sampling design
sys_design <- svydesign(id = ~1, data = policy, fpc = ~N)

#Which function will you use to obtain the estimator and its standard error? svymean or svytotal?
svymean(~FavorPolicy, design = sys_design)

#Find Confidence interval
0.66 - 2*0.0319
0.66 + 2*0.0319

#####By hand
N = 2000
n = 200
phat = 0.66
SD_prop = sqrt((phat*(1-phat)/(n-1))*((N-n)/N))
SD_prop
```

#Question 2
Reading the data set

```{r}
#volume = read.csv(file.choose()) # Volume
volume = read.csv("")

head(volume)
```

#2a
Create a scatterplot by filling in the code with the appropriate variables and labels

```{r}
plot(volume$Plot, volume$Volume, xlab = "Unit Element", ylab = "Volume")
```

#2c
Use the nrow(), mean() and sd() functions to get the summary measures

```{r}
mean(volume$Volume)
sd(volume$Volume)
nrow(volume)
```

#2d
```{r}
#Add a variable to the data set "policy" with the population size
volume$N = 520
head(volume)

#Specify sampling design
sys_design <- svydesign(id = ~1, data = volume, fpc = ~N)

#Which function will you use to obtain the estimator and its standard error? svymean or svytotal?
svymean(~Volume, design = sys_design)

#Find Confidence interval
7038.1 - 2*54.368
7038.1 + 2*54.368
```

#Question 3

Reading the data set
```{r}
#d = read.csv(file.choose()) #  Temp
d = read.csv("/Users/acaciamoran/Downloads/temp.csv")

head(d)
nrow(d)
```

#3a
Create a scatterplot by filling in the code with the appropriate variables and labels

```{r}
plot(d$Id, d$T, xlab = "Element Number", ylab = "Temperature")
```

#3b
Selecting a random number between 1 - 4
Selecting a random number between 1 - X. Change X for the correct number.

```{r}
sample(1:4, 1,replace = FALSE)
```

Creating a subset of the dataset

```{r}
#Creating vector with the starting point and the next elements
chosen = seq(from = 3, to = 80, by = 4)
chosen

#Creading a new subset of the data
sys_sample = d[chosen, ]
sys_sample
```

#3c
Find estimator and its standard error
```{r}
sys_sample$N = 80
sys_design <- svydesign(id = ~1, data = sys_sample, fpc = ~N)
svymean(~T, design = sys_design)
```

#3d
Selecting 4 random numbers between 1 - 16

```{r}
chosen_rep = sample(1:16, 4,replace = FALSE)
chosen_rep
```

Creating vector with the 4 starting points and the next elements

```{r}
samp1 = seq(from = 6, to = 80, by = 16)
samp2 = seq(from = 14, to = 80, by = 16)
samp3 = seq(from = 1, to = 80, by = 16)
samp4 = seq(from = 16, to = 80, by = 16)
```

#3e

Getting summary measures:
```{r}
samp1_values = d[samp1, ]
samp2_values = d[samp2, ]
samp3_values = d[samp3, ]
samp4_values = d[samp4, ]

repeat_data = rbind(samp1_values, samp1_values, samp3_values, samp4_values)
repeat_data

repeat_data$sample = c(rep(1,5), rep(2,5), rep(3,5), rep(4,5))
repeat_data

mean = tapply(repeat_data$T,repeat_data$sample,mean)
mean

sd(mean)
```


Calculating estimator

Create a formula in R to estimate the population mean in repeated systematic samples (see handout for the actual formula).


```{r}
ns = 4
ybar_sys = sum(mean)/ns
ybar_sys
```


Calculating variance of estimator

Create a formula in R to estimate the variance of the estimator above in repeated systematic samples (see handout for the actual formula)

```{r}
N = 80
n = 20
var_sys = (1-n/N)*(sd(mean)^2)/ns
var_sys
```

Calculating Confidence interval
```{r}
ybar_sys-2*sqrt(var_sys)
ybar_sys+2*sqrt(var_sys)
```

